
###############################################################################
# "Interplay between Childhood Trauma, Bodily Self-Disturbances, and Clinical 
#   Phenomena in Schizophrenia: a Network Analysis"    

# date 08/10/2023                                                            
###############################################################################


#Data available unpon request. 


#Load libraries

```{r}
library(tidyverse)
library(bootnet)
library(mgm)
library(dplyr)
library(EstimateGroupNetwork) 
library(qgraph)
library(reshape2)
library(NetworkComparisonTest)
library(scales)
library(raster)
library(useful)
library(psych)
library(networktools)
library(igraph)
library(EGAnet)
```


# *NETWORK 1* 

#Estimate network
```{r}
sxs_network <- estimateNetwork(data3, default="EBICglasso", corMethod="spearman") 
```


#Visualize
```{r}
sxs_network$labels<- c("PAS", "Emo\nAbuse", "Phys\nAbuse", "Sex\nAbuse", "Emo\nNeglect", "Phys\nNeglect",  "Positive", "Negative", "General") 
Groups <- c(rep("PAS",1),rep("CTQ",5),rep("PANSS",3))
colors<-c("lavender",  "lightcyan", "indianred1")


plot2<- qgraph(sxs_network$graph,
                layout = "spring",
                labels = sxs_network$labels, vsize=12,  pieColor = "lightgrey",  label.scale.equal=TRUE,label.cex=1.2, fade=FALSE, groups= Groups,  colors=colors)
```


#Stability coef
```{r}
nboots = 1000
caseN = 100
btnt <- list()
set.seed(1)
btnt$sxs_network<- bootnet(data3,
                         default = "EBICglasso",
                         type = "case",
                         nBoots = nboots,
                         caseN = caseN, nCores = 8)

corStability(btnt$sxs_network)
```



#Shortest paths between CTQ and sxs 
```{r}
SZ_sxs_paths<- pathways(plot2, from = c("Emo\nAbuse", "Phys\nAbuse", "Sex\nAbuse", "Emo\nNeglect", "Phys\nNeglect"), to = c("Positive", "Negative", "General"), fading = 0.25, lty = 3)
```




# Community detection with EGA
```{r}
EGA(data3, plot.EGA = TRUE, corr= "spearman", algorithm = "walktrap") 
```


#Bridge based on EGA communities 
```{r}
# With 2 communities (based on EGA)
b2 <- bridge(plot2, communities=c('1', '1', '1', '1', '1', '1', '2', '2', '2'))
b2
```





# NETWORK 1 SUPPLEMENTARY ANALYSES


#Centrality indices
```{r}
centralityplot<-centralityPlot(sxs_network, include= c("Strength", "ExpectedInfluence", "Closeness", "Betweenness"),
               orderBy ="Strength") 
```


# Node predictability
```{r}
type=rep('g', 9) 
fit10 <- mgm(data=data3, type=type, lev=rep(1,9), d=1) 
pred10 <- predict(fit10,data3, error.continuous='VarExpl')  
mean(pred10$error$R2) 
```


#Visualize with predictability
```{r}
plot2 <- qgraph(sxs_network$graph,
                layout = "spring",
                labels = sxs_network$labels, vsize=12,  pieColor = "lightgrey", pie=pred10$error$R2, label.scale.equal=TRUE,label.cex=1.2, fade=FALSE, groups= Groups,  colors=colors)
```

# Confidence intervals 
```{r}
sxs_network$labels<- c("PAS", "Emo Abuse", "Phys Abuse", "Sex Abuse", "Emo Neglect", "Phys Neglect",  "Positive", "Negative", "General") 

boot1 <- bootnet(sxs_network, nCores = 8,
                 nBoots = 1000, type = "nonparametric")

plot(boot1, plot = "interval", order="sample") 
```












# *NETWORK 2 *

#Estimate Network
```{r}
pos_sxs_network <- estimateNetwork(data4, default="EBICglasso", corMethod= "spearman") 
```

#Visualize
```{r}

pos_sxs_network$labels<- c("PAS", "Emo\nAbuse", "Phys\nAbuse", "Sex\nAbuse", "Emo\nNeglect", "Phys\nNeglect",  "Delusions", "Disorg.", "Hallu.", "Excitement", "Grandiosity", "Suspicion", "Hostility") 
Groups <- c(rep("PAS",1),rep("CTQ",5),rep("PANSS positive",7))
colors<-c("lavender",  "lightcyan", "indianred1")

plot3 <- qgraph(pos_sxs_network$graph, 
                layout = "spring",
                labels = pos_sxs_network$labels, vsize=12,  label.scale.equal=TRUE,label.cex=1.2, fade=FALSE, groups= Groups,  colors=colors)
```


#Stability coef
```{r}
nboots = 1000
caseN = 100
btnt <- list()
set.seed(1)
btnt$pos_sxs_network<- bootnet(data4,
                         default = "EBICglasso",
                         type = "case",
                         nBoots = nboots,
                         caseN = caseN, nCores = 8)

corStability(btnt$pos_sxs_network) 
```



#Shortest paths between CTQ and positive sxs 
```{r}
SZ_positivesxs_path<- pathways(plot3, from= c("Emo\nAbuse", "Phys\nAbuse", "Sex\nAbuse", "Emo\nNeglect", "Phys\nNeglect"), to = c("Delusions", "Disorg.", "Hallu.", "Excitement", "Grandiosity", "Suspicion", "Hostility") , fading = 0.25, lty = 3)
```


#EGA
```{r}
EGA(data4, plot.EGA = TRUE)
```

#bridge

```{r}

b2 <- bridge(plot3, communities=c('2', '2', '2', '2', '2', '2', '1', '1', '1' , '1' , '1' , '1' ,'1'))
b2
```




#NETWORK 2 SUPPLEMENTARY ANALYSES

#Centrality indices
```{r}
centralityplot<-centralityPlot(pos_sxs_network, include= c("Strength", "ExpectedInfluence", "Closeness", "Betweenness"),
               orderBy ="Strength") 
```



# Node predictability
```{r}
type=rep('g', 13) 
fit11 <- mgm(data=data4, type=type, lev=rep(1,13), d=1) 
pred11 <- predict(fit11,data4, error.continuous='VarExpl')  
mean(pred11$error$R2)  #0.40
```

#Visualize with predictability
```{r}
plot4 <- qgraph(pos_sxs_network$graph,
                layout = "spring", pieColor = "lightgrey", pie=pred11$error$R2,
                labels = pos_sxs_network$labels, vsize=12,  label.scale.equal=TRUE,label.cex=1.2, fade=FALSE, groups= Groups,  colors=colors)
```


# Confidence intervals for the pathway to test wether it is significantly non-zero
```{r}
pos_sxs_network$labels<- c("PAS", "Emo Abuse", "Phys Abuse", "Sex Abuse", "Emo Neglect", "Phys Neglect",  "Delusions", "Disorg.", "Hallu.", "Excitement", "Grandiosity", "Suspicion", "Hostility") 

boot2 <- bootnet(pos_sxs_network, nCores = 8,
                 nBoots = 1000, type = "nonparametric")
plot(boot2, plot = "interval", order="sample") 

```









*NETWORK 3*

#Estimate Network
```{r}
distress_sxs_network <- estimateNetwork(data5, default="EBICglasso", corMethod= "spearman") 
```


#Visualize
```{r}
distress_sxs_network$labels<- c("PAS", "Emo\nAbuse", "Phys\nAbuse", "Sex\nAbuse", "Emo\nNeglect", "Phys\nNeglect", "Anxiety", "Depression", "Guilt", "Tension")

Groups <- c(rep("PAS",1),rep("CTQ",5),rep("PANSS distress",4))
colors<-c("lavender",  "lightcyan", "indianred1")

plot5 <- qgraph(distress_sxs_network$graph, layout= "spring",  
                labels = distress_sxs_network$labels, vsize=12,  label.scale.equal=TRUE,label.cex=1.2, fade=FALSE, groups= Groups,  colors=colors) 
```

#Stability coef
```{r}
nboots = 1000
caseN = 100
btnt <- list()

set.seed(1)
btnt$distress_sxs_network<- bootnet(data5,
                         default = "EBICglasso",
                         type = "case",
                         nBoots = nboots,
                         caseN = caseN, nCores = 8)

corStability(btnt$distress_sxs_network)
```






#Shortest paths between CTQ and distress sxs 
```{r}
SZ_distresssxs_path<- pathways(plot5, from= c("Emo\nAbuse", "Phys\nAbuse", "Sex\nAbuse", "Emo\nNeglect", "Phys\nNeglect"), to = c("Anxiety", "Depression", "Guilt", "Tension") , fading = 0.25, lty = 3)
```

# Confidence intervals 
```{r}
distress_sxs_network$labels<- c("PAS", "Emo Abuse", "Phys Abuse", "Sex Abuse", "Emo Neglect", "Phys Neglect",  "Anxiety", "Depression", "Guilt", "Tension") 

boot5 <- bootnet(distress_sxs_network, nCores = 8,
                 nBoots = 1000, type = "nonparametric")
plot(boot5, plot = "interval", order="sample") 
```



#EGA
```{r}
EGA(data5, plot.EGA = TRUE) 
```

#bridge
```{r}
b5 <- bridge(plot5, communities=c('2', '3', '2', '2', '3', '3', '4', '1', '1', '4'))
b5
plot(b5)
```


# NETWORK 3 SUPPLEMENTARY ANALYSES


#Centrality indices
```{r}
centralityplot<-centralityPlot(distress_sxs_network, include= c("Strength", "ExpectedInfluence", "Closeness", "Betweenness"),
               orderBy ="Strength") 
```


# Node predictability
```{r}
type=rep('g', 10) 
fit11 <- mgm(data=data5, type=type, lev=rep(1,10), d=1) 
pred11 <- predict(fit11,data5, error.continuous='VarExpl')  
mean(pred11$error$R2) 
```

#Visualize with predictability
```{r}
plot4 <- qgraph(distress_sxs_network$graph,
                layout = "spring", pieColor = "lightgrey", pie=pred11$error$R2,
                labels = distress_sxs_network$labels, vsize=12,  label.scale.equal=TRUE,label.cex=1.2, fade=FALSE, groups= Groups,  colors=colors)
```




